Rising from the Ashes: A Metallicity-Dependent Star Formation Gap Splits the Milky Way's $\alpha$-Sequences

### 2025-02-13 paper/ms.tex
Update surface density section

\section{Results}\label{sec:results}
\subsection{Surface Density Projections}\label{ssec:projections}
Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy in the bimodal simulation. This is shown in Figure~\ref{fig:projections}. In each grouping of four, the bottom and top rows show the face-on and edge-on views, respectively. The left and right columns show the gas (blue) and stellar (orange) surface density, respectively. Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$). The angular momentum is computed using all star particles within the half-mass radius.

@@

    \gridline{\fig{all_L30_frame60.pdf}{0.3\textwidth}{}
              \fig{all_L30_frame70.pdf}{0.3\textwidth}{}
              \fig{all_L30_frame80.pdf}{0.3\textwidth}{}
              }
    \gridline{\fig{all_L30_frame90.pdf}{0.3\textwidth}{}
              \fig{all_L30_frame100.pdf}{0.3\textwidth}{}
              \fig{all_L30_frame110.pdf}{0.3\textwidth}{}
              }
    \gridline{\fig{all_L30_frame120.pdf}{0.3\textwidth}{}
              \fig{all_L30_frame200.pdf}{0.3\textwidth}{}
              \fig{all_L30_frame320.pdf}{0.3\textwidth}{}
              }
  % \includegraphics[width=\textwidth]{surfdens.pdf}
  \caption{Frames from a movie showing a surface density projection of the bimodal simulation over time. In each frame, the left/right (blue/orange) column shows the gas/star surface density. The upper/lower panels show the edge-on and face-on view. Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot. The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length. The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$. (A full movie is \href{https://drive.google.com/file/d/1RKpFpnFIpl7XYAX5lvF7CyaPVO5dS3EO/view?usp=drive_link}{here}.)}
  \label{fig:projections}
\end{figure*}

>>>>

\section{Results}\label{sec:results}
\subsection{Surface Density Projections}\label{ssec:projections}
Before dissecting the simulated galaxies in detail, we first examine the surface density projections of the gas and stars in the central region, situated on the central galaxy in the bimodal simulation. This is shown in Figure~\ref{fig:projections}. In each grouping of four, the bottom and top rows show the face-on and edge-on views, respectively. The left and right columns show the gas (blue) and stellar (orange) surface density, respectively. Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$), computed using all star particles within the half-mass radius.

@@

    \gridline{\fig{bimodal_L30_frame60.pdf}{0.3\textwidth}{}
              \fig{bimodal_L30_frame70.pdf}{0.3\textwidth}{}
              \fig{bimodal_L30_frame80.pdf}{0.3\textwidth}{}
              }
    \gridline{\fig{bimodal_L30_frame90.pdf}{0.3\textwidth}{}
              \fig{bimodal_L30_frame100.pdf}{0.3\textwidth}{}
              \fig{bimodal_L30_frame110.pdf}{0.3\textwidth}{}
              }
    \gridline{\fig{bimodal_L30_frame120.pdf}{0.3\textwidth}{}
              \fig{bimodal_L30_frame200.pdf}{0.3\textwidth}{}
              \fig{bimodal_L30_frame320.pdf}{0.3\textwidth}{}
              }
  \caption{Frames from a movie showing a surface density projection of the bimodal simulation over time. In each frame, the left/right (blue/orange) column shows the gas/star surface density. The upper/lower panels show the edge-on and face-on view. Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot. The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length. The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$. \edit1{Description of movie: The disk collapses quickly, forming a disk within $500\,\Myr$. The satellite galaxy quickly passes in the background at $\sim700\,\Myr$. At $\sim2\,\Gyr$, the satellite directly merges with the central galaxy, fully coalescing by $\sim3\,\Gyr$. Over the next $5\,\Gyr$, the disk steadily grows, expanding in size.} (A full movie is \edit1{linked in submission}.)}
  \label{fig:projections}
\end{figure*}
